ManuscriptTargetProtein

### 2024-02-29 Code/ManuscriptTargetProtein.Rmd
standardized variable names for ggplot labels across rmds

MIT9313ProteinAnnotated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
 labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
  # scale_fill_manual(fill = (O2_uM)) %>% 
  # scale_colour_manual(values = ColourOxygen) +
 ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
 # guides(fill = "none") +
  theme_bw()

@@

MED4ProteinAnnotated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
 labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
  # scale_fill_manual(fill = (O2_uM)) %>% 
  # scale_colour_manual(values = ColourOxygen) +
 ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
 # guides(fill = "none") +
  theme_bw()

>>>>

MIT9313ProteinAnnotated <- TargetProtein %>%
  filter(Strain == "MIT9313") %>% 
   mutate(OxygenLabel = "Oxygen Concentration (µM)",
         ParLabel = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
        O2_uM = factor(O2_uM, levels = c("250", "2.5")),
        ParLabel = factor(ParLabel, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
   ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
  geom_col(position="Dodge") +
   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black")  +
 labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
  scale_fill_manual(values = MCMIXColours) +
  scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, ParLabel ), rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(O2_uM = label_value, WL = label_both, O2 = label_both, Strain = label_value)) +
guides(color = "none") +
  theme_bw() +
  theme(legend.position = "top") +
  labs(fill = "Growth Waveband (nm)")

@@

MED4ProteinAnnotated <- TargetProtein %>%
  filter( Strain == "MED4",
          O2_uM != 2.5) %>% 
   mutate(OxygenLabel = "Oxygen Concentration (µM)",
         ParLabel = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
        O2_uM = factor(O2_uM, levels = c("250", "2.5")),
        ParLabel = factor(ParLabel, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
  geom_col(position="Dodge") +
   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)), na.rm=FALSE ,  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
 labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
  scale_fill_manual(values = MCMIXColours) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, ParLabel ), rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(O2_uM = label_value, WL = label_both, O2 = label_both, Strain = label_value)) +
guides(color = "none") +
  theme_bw() +
  theme(legend.position = "top") +
  labs(fill = "Growth Waveband (nm)")
